Analysis, Prototyping and Locomotion Control of a Quadruped Robot\\

### 2023-06-18 LARS_paper/paper.tex
Add tf2 ref and fix images positions

%TODO cite tf2
The package tf2, an available ROS 2 feature that can manage transformations between coordinate axes, was used to solve the robot's forward kinematics, and the inverse kinematics was solved based on geometric analysis. The variables $\theta_1$, $\theta_2$ and $\theta_3$ express the angular position of each leg joint (angles of hip, femur and tibia, respectively), and they can be calculated with the help of \eqref{eq:theta1} to \eqref{eq:B}, as a function of the desired position of the foot w.r.t. to the hip link $(x_{IK}, y_{IK}, z_{IK})$ and the lengths $L_1$, $L_2$ and $L_3$ (Fig. \ref{fig:caramel_tfs}).

@@

\begin{figure}[b]
  \centering
  \begin{subfigure}[htbp]{0.24\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{terreno_plano.jpeg}
    \caption{Flat.}
    \label{fig:terreno_plano}
  \end{subfigure}
  \begin{subfigure}[htbp]{0.24\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{terreno_irregular.jpeg}
    \caption{Uneven.}
    \label{fig:terreno_uneven}
  \end{subfigure}
  \vfill
  \caption{Terrains used for the experiment.}
  \label{fig:terrenos}
\end{figure}

@@

\begin{table}[!htb]
  \centering
  \caption{Velocity and stability results.}
  \scalebox{1.3}{
  \begin{tabular}{ccccc}
    \hline
    \textbf{Test}              & \textbf{1}   & \textbf{2}  & \textbf{3}   & \textbf{4}   \\ \hline
    Ter.                       & Flat         & Flat        & Uneven       & Uneven       \\ \hline
    \begin{tabular}[c]{@{}c@{}}S. C. \end{tabular} & No           & Yes         & No           & Yes          \\ \hline
    \begin{tabular}[c]{@{}c@{}}Vel. \\ $(cm/s)$ \end{tabular} & 2.15         & 3.68        & 2.03         & 2.39         \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Vel}$  \\ $(cm/s)$ \end{tabular} & 0.040        & 0.075       & 0.016        & 0.047        \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Roll}$ \end{tabular} & 12.59\degree & 8.81\degree & 13.37\degree & 11.13\degree \\\hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Roll}$ \end{tabular} & 2.54\degree  & 2.36\degree & 0.78\degree  & 1.47\degree  \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Pitch}$ \end{tabular} & 11.55\degree & 8.31\degree & 15.19\degree & 12.09\degree \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Pitch}$ \end{tabular} & 1.89\degree  & 2.63\degree & 1.44\degree  & 1.66\degree  \\ \hline
  \end{tabular}
  }
  \label{tab:vel_stab}
  \vspace{-\baselineskip}
\end{table}

@@

\begin{figure}[!tb]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{plane_boxplot.png}
    \caption{Flat terrain.}
    \label{fig:imu_test_plane}
  \end{subfigure}
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{irregular_boxplot.png}
    \caption{Uneven terrain.}
    \label{fig:imu_test_irregular}
  \end{subfigure}
  \caption{Robot body's oscillation in both terrains.}
  \label{fig:imu_test}
\end{figure}

@@

The robot's project is open source and is available on GitHub \cite{CaramelRepo}.

>>>>

The package tf2 \cite{tf2}, an available ROS 2 feature that can manage transformations between coordinate axes, was used to solve the robot's forward kinematics, and the inverse kinematics was solved based on geometric analysis. The variables $\theta_1$, $\theta_2$ and $\theta_3$ express the angular position of each leg joint (angles of hip, femur and tibia, respectively), and they can be calculated with the help of \eqref{eq:theta1} to \eqref{eq:B}, as a function of the desired position of the foot w.r.t. to the hip link $(x_{IK}, y_{IK}, z_{IK})$ and the lengths $L_1$, $L_2$ and $L_3$ (Fig. \ref{fig:caramel_tfs}).

@@

\begin{figure}[tb]
  \centering
  \begin{subfigure}[htbp]{0.24\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{terreno_plano.jpeg}
    \caption{Flat.}
    \label{fig:terreno_plano}
  \end{subfigure}
  \begin{subfigure}[htbp]{0.24\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{terreno_irregular.jpeg}
    \caption{Uneven.}
    \label{fig:terreno_uneven}
  \end{subfigure}
  \vfill
  \caption{Terrains used for the experiment.}
  \label{fig:terrenos}
  \vspace{-\baselineskip}
\end{figure}

@@

\begin{table}[!htb]
  \centering
  \caption{Velocity and stability results.}
  \scalebox{1.3}{
  \begin{tabular}{ccccc}
    \hline
    \textbf{Test}              & \textbf{1}   & \textbf{2}  & \textbf{3}   & \textbf{4}   \\ \hline
    Ter.                       & Flat         & Flat        & Uneven       & Uneven       \\ \hline
    \begin{tabular}[c]{@{}c@{}}S. C. \end{tabular} & No           & Yes         & No           & Yes          \\ \hline
    \begin{tabular}[c]{@{}c@{}}Vel. \\ $(cm/s)$ \end{tabular} & 2.15         & 3.68        & 2.03         & 2.39         \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Vel}$  \\ $(cm/s)$ \end{tabular} & 0.040        & 0.075       & 0.016        & 0.047        \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Roll}$ \end{tabular} & 12.59\degree & 8.81\degree & 13.37\degree & 11.13\degree \\\hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Roll}$ \end{tabular} & 2.54\degree  & 2.36\degree & 0.78\degree  & 1.47\degree  \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\Delta_{Pitch}$ \end{tabular} & 11.55\degree & 8.31\degree & 15.19\degree & 12.09\degree \\ \hline
    \begin{tabular}[c]{@{}c@{}} $\sigma_{Pitch}$ \end{tabular} & 1.89\degree  & 2.63\degree & 1.44\degree  & 1.66\degree  \\ \hline
  \end{tabular}
  }
  \label{tab:vel_stab}
  % \vspace{-\baselineskip}
\end{table}

@@

\begin{figure}[!b]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{plane_boxplot.png}
    \caption{Flat terrain.}
    \label{fig:imu_test_plane}
  \end{subfigure}
  \begin{subfigure}[t]{0.49\textwidth}
    \centering
    \includegraphics[width=1.0\textwidth]{irregular_boxplot.png}
    \caption{Uneven terrain.}
    \label{fig:imu_test_irregular}
  \end{subfigure}
  \caption{Robot body's oscillation in both terrains.}
  \label{fig:imu_test}
  \vspace{-1.5\baselineskip}
\end{figure}

@@

The robot's project is open source and is available on GitHub [Blinded reference]. % \cite{CaramelRepo}.
